%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Robert Skelton} % Your name
\address{1074 Citrus Ave NE \\ Palm Bay, FL 32905 \\ (321)~$\cdot$~616~$\cdot$~3617} % Your address
\address{robertjskelton@gmail.com \\ skelton.co \\ github.com/robertjskelton} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

%------------------------------------------------

\begin{rSubsection}{GE Digital}{February 2017 - Present}{DevOps Engineer / Cloud Architect}{Palm Bay, FL}
\item Lead deployment and automation efforts to cut \$50,000+ per year in data centers costs.
\item Collaborated with international teams to deliver highly available and scalable applications.
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Harris Corporation}{June 2015 - February 2017}{Information Security Systems Engineer/Unix Systems Administrator}{Melbourne, FL}
\item Technical lead for FTI's Compliance, Auditing and Verification Team.
\item Lead multi-disciplined deployment of Tenable Security Suite to 20+ remote FAA sites.
\item Developed cross-platform scripts to reduce workload up to 80\%.
\item Provided Tier 2 support on Linux and Solaris servers and workstations.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Oak Ridge National Laboratory}{June 2013 - August 2013}{Cyber and Information Security Research Intern}{Oak Ridge, TN}
\item Developed a process for creating a Cyber Range using XenServer, multiple virtual machines, and virtual and physical networking.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{VT Miltope}{August 2011 - May 2013}{Test Engineering Co-op}{Hope Hull, AL}
\item Developed an understanding of manufacturing and business processes while developing technical skills.
\item Tested, troubleshot, replaced and improved many computer components, including: motherboards, displays, keyboards, RAM, bezels, power supplies, I/O ports, and disc drives.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Georgia Institute of Technology} \hfill {\em January 2016 - May 2019(est)} \\
M.S. in Computer Science \\
Specialization in Computing Systems
\smallskip

{\bf Auburn University} \hfill {\em August 2010 - May 2015} \\
B.S. in Computer Engineering, GPA: 3.40 \\
Founder/President, Auburn University Linux Club \\
Webmaster, Auburn University Eta Kappa Nu \\
Director of Communications, Auburn University IEEE Student Branch \\
Global Datafest Hackathon, Organizer (2015), Participant (2013, 2015) \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Certifications & AWS Certified Solutions Architect, Security+, Linux+, LPIC-1, SUSE CLA \\
DevOps & Amazon Web Services, Chef, Jenkins, Scalr, Databases \\
Programming & Java, C/C++, Python, Javascript, bash, HTML, SQL \\
OS/Apps & Multiple Linux Distributions, Android, OS X, Virtualbox, VMWare, Wordpress \\
Tools & Microsoft Office Suite, Tenable SecurityCenter, Eclipse, Git, Vim, JUnit, Atom \\
Other & Enterprise Architecture, Computer Hardware, Software Development Lifecycle \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
